Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-13 tex/sections/consensus.tex
Improve readability of "Emergency Agreement"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

A honest user during a round only votes a single proposal. This ensures that as long as more than $2/3$ of the total
stake of the system is controlled by honest users, no two different proposals can get more than $2/3$ votes. Also, he
either votes $p$-win or $draw$, so only one of $p$-win or $draw$ can get more than $2/3$ votes. Consequently, when a
user sees more than $2/3$ $p$-win votes, he can be sure that $draw$ has less than $2/3$ votes. Therefore, for going
to the next round we will need 2/3 $p$-lock
votes and all honest users will lock their vote on $p$ when they start the next round. As a result only $p$ can be
confirmed by the agreement protocol.

When a single honest user terminates the protocol, he can convince all other honest users to terminate their protocol
by sending those 2/3 $p$-win votes that he has seen.

>>>>

A honest user during a round only votes a single proposal. This ensures that as long as more than $2/3$ of the total
stake of the system is controlled by honest users, no two different proposals can get more than $2/3$ votes.
As a result, we can not have 2/3 votes for both $p$-lock and $p'$-lock if $p \neq p'$. Also, a honest user
either votes $p$-win or $draw$, so only one of $p$-win or $draw$ can get more than $2/3$ votes and when a
user sees more than $2/3$ $p$-win votes, he can be sure that $draw$ has less than $2/3$ votes. Therefore, for going
to the next round we will need 2/3 $p$-lock
votes and all honest users will lock their vote on $p$ when they start the next round. As a result only $p$ can be
confirmed by the agreement protocol.

Note that when a single honest user terminates the protocol, he can convince all other honest users to terminate
their protocol by sending those 2/3 $p$-win votes that he has seen.
